Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-30 Scripts/Initial_Analysis.Rmd
Included dummy data for F1 toe

>>>>

## Figures for F1

This is a hypothetical figure to show the idea behind the ToE. It does not follow the actual method but only shows the trend.

```{r tsi_figure, eval = F}

# Create dummy data
dummy_data <- data.frame(
  year = seq(1951,2100,1),
  tsi = c(runif(80,-10,10),
          runif(20,-10,4),
          runif(30,-12,0),
          runif(20,-14,-4)),
  tsia = c(runif(80,-10,10),
          runif(20,-10,4),
          runif(30,-12,0),
          runif(20,-14,-4)),
  tsib = c(runif(80,-10,10),
           runif(20,-10,4),
           runif(30,-12,0),
           runif(20,-14,-4)),
  tsic = c(runif(80,-10,10),
           runif(20,-10,4),
           runif(30,-12,0),
           runif(20,-14,-4))
) %>% 
    rowwise() %>% 
    mutate(
      mean_tsi = mean(c(tsi,tsia,tsib,tsic),na.rm=T)
    ) %>% 
    ungroup() %>% 
  group_by() %>% 
  mutate_all(funs(zoo::rollmean(., 
                          10, 
                          align = "left", 
                          fill = NA,
                          na.rm=T)
  )) %>% 
  gather("eme","value",tsi:tsic)

# Get min, max and toe for box/noise
min <- dummy_data %>% 
  filter(year < 2006) %>% 
  pull(value) %>% 
  min()

max <- dummy_data %>% 
  filter(year < 2006) %>% 
  pull(value) %>% 
  max()

# ToE
toe <- dummy_data %>% 
  filter(year > 2005 & mean_tsi < min+0.5) %>% 
  slice(1)

# Make hypotetical figure
ggplot(dummy_data) +
  # Historical variation box (noise)
  geom_rect(
    aes(xmin=1951,
        xmax=2100,
        ymin=min+0.5,
        ymax=max-1),
    fill="grey80",
    alpha = 0.5
  ) +
  # Historical mean
  geom_rect(
    aes(xmin=1951,
            xmax=2100,
            ymin = mean(c(min,max)),
            ymax = mean(c(min,max)),
            ),
    color = "grey60",
    size = 0.1
    ) +
  # Each ensemle
  geom_line(
    aes(
      x = year,
      y = value,
      fill = eme
    ),
    alpha = 0.8,
    color = "#F8AFA8"
  ) +
  # Average of ensembles (trend)
  geom_line(
    aes(
      x = year,
      y = mean_tsi
    ),
    color = "black"
  ) +
  # Mark ToE
  geom_point( data = toe,
    aes(
      x = year,
      y = mean_tsi
    ),
    color = "#FF0000",
    size = 5,
    alpha = 0.8
  ) +
  # Historical / Future division line
  geom_vline(xintercept = 2005, color = "#046C9A") +
  # Aesthetics
  scale_color_brewer(palette = "Oranges") +
  theme_classic()+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())+
  labs(x = "Transboundary shift index (TSI)",
       y = "Year")

# save image
ggsave(
  filename = "./Figures/tsi_fig.png",
  plot = last_plot(),
  width = 8,
  height = 4
)
